---
title: "Supplementary Materials: Clade-Specific Analyses"
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
header-includes:
- \usepackage{float}
- \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", out.width = "100%")
library(magick)

# Paths to plot folders
contmap_path <- "../../figures/clade figures/contmaps"
prior_post_path <- "../../figures/clade figures/clade_audit_plots"
adeq_path <- "../../figures/clade figures/adeq.plots"

# Function to create 2x2 panel figure with labels
create_panel_figure <- function(clade_name) {
  clade_lower <- tolower(clade_name)
  
  # File paths
  f_contmap <- file.path(contmap_path, paste0(clade_lower, "_CM.png"))
  f_prior   <- file.path(prior_post_path, paste0(clade_lower, "_audit.png"))
  f_var     <- file.path(adeq_path, paste0(clade_lower, ".PPS.csv_variance.png"))
  f_ent     <- file.path(adeq_path, paste0(clade_lower, ".PPS.csv_entropy.png"))
  
  # Read images
  img_a <- image_read(f_contmap)
  img_b <- image_read(f_prior)
  img_c <- image_read(f_var)
  img_d <- image_read(f_ent)
  
  # Get dimensions for label positioning
  info_a <- image_info(img_a)
  info_b <- image_info(img_b)
  info_c <- image_info(img_c)
  info_d <- image_info(img_d)
  
  # Add labels (white background box with black text, upper left)
  label_style <- "font-size: 48px; font-weight: bold;"
  
  img_a <- image_annotate(img_a, "A", size = 120, weight = 700,
                          location = "+20+10", color = "black",
                          boxcolor = "white")
  img_b <- image_annotate(img_b, "B", size = 60, weight = 700,
                          location = "+20+10", color = "black",
                          boxcolor = "white")
  img_c <- image_annotate(img_c, "C", size = 60, weight = 700,
                          location = "+20+10", color = "black",
                          boxcolor = "white")
  img_d <- image_annotate(img_d, "D", size = 60, weight = 700,
                          location = "+20+10", color = "black",
                          boxcolor = "white")
  
  # Resize all to same dimensions for consistent grid
  target_size <- "750x750!"
  img_a <- image_resize(img_a, target_size)
  img_b <- image_resize(img_b, target_size)
  img_c <- image_resize(img_c, target_size)
  img_d <- image_resize(img_d, target_size)
  
  # Create rows
  row1 <- image_append(c(img_a, img_b))
  row2 <- image_append(c(img_c, img_d))
  
  # Stack rows
  panel <- image_append(c(row1, row2), stack = TRUE)
  
  return(panel)
}
```

\newpage

# Bryophyta

## Bryophyta

Bryophyta | Higher Taxonomy: Bryophyta | Chromosomes sampled: 4,666 | Phylogenetic tips: 533 | Overlap with reference: 239 species | Root age: 488 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r bryophyta-fig, fig.cap="Validation plots for Bryophyta. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Bryophyta")
```

\newpage

# Pteridophyta

## Pteridophyta

Pteridophyta | Higher Taxonomy: Pteridophyta | Chromosomes sampled: 12,075 | Phylogenetic tips: 5,868 | Overlap with reference: 1,465 species | Root age: 429 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r pteridophyta-fig, fig.cap="Validation plots for Pteridophyta. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Pteridophyta")
```

\newpage

# Gymnospermae

## Gymnospermae

Gymnospermae | Higher Taxonomy: Gymnospermae | Chromosomes sampled: 2,026 | Phylogenetic tips: 31,749 | Overlap with reference: 375 species | Root age: 304 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r gymnospermae-fig, fig.cap="Validation plots for Gymnospermae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Gymnospermae")
```

\newpage

# Angiospermae

## Asteraceae

Asteraceae | Higher Taxonomy: Angiospermae | Chromosomes sampled: 6,497 | Phylogenetic tips: 3,336 | Overlap with reference: 3,336 species | Root age: 160 Ma | Taxonomic tips: TRUE | Unresolved: 21.52%

```{r asteraceae-fig, fig.cap="Validation plots for Asteraceae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Asteraceae")
```

\newpage

## Brassicaceae

Brassicaceae | Higher Taxonomy: Angiospermae | Chromosomes sampled: 2,822 | Phylogenetic tips: 1,557 | Overlap with reference: 1,557 species | Root age: 118 Ma | Taxonomic tips: TRUE | Unresolved: 45.02%

```{r brassicaceae-fig, fig.cap="Validation plots for Brassicaceae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Brassicaceae")
```

\newpage

## Fabaceae

Fabaceae | Higher Taxonomy: Angiospermae | Chromosomes sampled: 2,006 | Phylogenetic tips: 1,692 | Overlap with reference: 1,692 species | Root age: 68 Ma | Taxonomic tips: TRUE | Unresolved: 55.56%

```{r fabaceae-fig, fig.cap="Validation plots for Fabaceae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Fabaceae")
```

\newpage

## Liliaceae

Liliaceae | Higher Taxonomy: Angiospermae | Chromosomes sampled: 648 | Phylogenetic tips: 79,340 | Overlap with reference: 430 species | Root age: 119 Ma | Taxonomic tips: TRUE | Unresolved: 18.14%

```{r liliaceae-fig, fig.cap="Validation plots for Liliaceae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Liliaceae")
```

\newpage

## Magnoliaceae

Magnoliaceae | Higher Taxonomy: Angiospermae | Chromosomes sampled: 139 | Phylogenetic tips: 304 | Overlap with reference: 77 species | Root age: 42 Ma | Taxonomic tips: TRUE | Unresolved: 59.74%

```{r magnoliaceae-fig, fig.cap="Validation plots for Magnoliaceae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Magnoliaceae")
```

\newpage

## Orchidaceae

Orchidaceae | Higher Taxonomy: Angiospermae | Chromosomes sampled: 8,122 | Phylogenetic tips: 41,474 | Overlap with reference: 1,904 species | Root age: 17 Ma | Taxonomic tips: TRUE | Unresolved: 43.22%

```{r orchidaceae-fig, fig.cap="Validation plots for Orchidaceae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Orchidaceae")
```

\newpage

## Passifloraceae

Passifloraceae | Higher Taxonomy: Angiospermae | Chromosomes sampled: 159 | Phylogenetic tips: 134 | Overlap with reference: 134 species | Root age: 50 Ma | Taxonomic tips: TRUE | Unresolved: 26.12%

```{r passifloraceae-fig, fig.cap="Validation plots for Passifloraceae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Passifloraceae")
```

\newpage

## Rubiaceae

Rubiaceae | Higher Taxonomy: Angiospermae | Chromosomes sampled: 1,219 | Phylogenetic tips: 794 | Overlap with reference: 794 species | Root age: 72 Ma | Taxonomic tips: TRUE | Unresolved: 53.90%

```{r rubiaceae-fig, fig.cap="Validation plots for Rubiaceae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Rubiaceae")
```

\newpage

## Solanaceae

Solanaceae | Higher Taxonomy: Angiospermae | Chromosomes sampled: 1,458 | Phylogenetic tips: 930 | Overlap with reference: 930 species | Root age: 51 Ma | Taxonomic tips: TRUE | Unresolved: 48.28%

```{r solanaceae-fig, fig.cap="Validation plots for Solanaceae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Solanaceae")
```

\newpage

# Fungi

## Fungi

Fungi | Higher Taxonomy: Fungi | Chromosomes sampled: 151 | Phylogenetic tips: 5,418 | Overlap with reference: 40 species | Root age: 642 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r fungi-fig, fig.cap="Validation plots for Fungi. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Fungi")
```

\newpage

# Insecta

## Blattodea

Blattodea | Higher Taxonomy: Insecta | Chromosomes sampled: 190 | Phylogenetic tips: 151 | Overlap with reference: 30 species | Root age: 270 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r blattodea-fig, fig.cap="Validation plots for Blattodea. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Blattodea")
```

\newpage

## Phasmatodea

Phasmatodea | Higher Taxonomy: Insecta | Chromosomes sampled: 109 | Phylogenetic tips: 148 | Overlap with reference: 11 species | Root age: 140 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r phasmatodea-fig, fig.cap="Validation plots for Phasmatodea. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Phasmatodea")
```

\newpage

## Orthoptera

Orthoptera | Higher Taxonomy: Insecta | Chromosomes sampled: 319 | Phylogenetic tips: 232 | Overlap with reference: 36 species | Root age: 74 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r orthoptera-fig, fig.cap="Validation plots for Orthoptera. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Orthoptera")
```

\newpage

## Hemiptera

Hemiptera | Higher Taxonomy: Insecta | Chromosomes sampled: 1,744 | Phylogenetic tips: 1,967 | Overlap with reference: 46 species | Root age: 258 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r hemiptera-fig, fig.cap="Validation plots for Hemiptera. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Hemiptera")
```

\newpage

## Hymenoptera

Hymenoptera | Higher Taxonomy: Insecta | Chromosomes sampled: 1,591 | Phylogenetic tips: 602 | Overlap with reference: 345 species | Root age: 240 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r hymenoptera-fig, fig.cap="Validation plots for Hymenoptera. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Hymenoptera")
```

\newpage

## Dytiscidae

Dytiscidae | Higher Taxonomy: Insecta | Chromosomes sampled: 85 | Phylogenetic tips: 973 | Overlap with reference: 29 species | Root age: 144 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r dytiscidae-fig, fig.cap="Validation plots for Dytiscidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Dytiscidae")
```

\newpage

## Carabidae

Carabidae | Higher Taxonomy: Insecta | Chromosomes sampled: 777 | Phylogenetic tips: 104 | Overlap with reference: 95 species | Root age: 103 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r carabidae-fig, fig.cap="Validation plots for Carabidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Carabidae")
```

\newpage

## Hydrophilidae

Hydrophilidae | Higher Taxonomy: Insecta | Chromosomes sampled: 81 | Phylogenetic tips: 168 | Overlap with reference: 21 species | Root age: 133 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r hydrophilidae-fig, fig.cap="Validation plots for Hydrophilidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Hydrophilidae")
```

\newpage

## Scarabidae

Scarabidae | Higher Taxonomy: Insecta | Chromosomes sampled: 478 | Phylogenetic tips: 211 | Overlap with reference: 174 species | Root age: 180 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r scarabidae-fig, fig.cap="Validation plots for Scarabidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Scarabidae")
```

\newpage

## Coccinellidae

Coccinellidae | Higher Taxonomy: Insecta | Chromosomes sampled: 159 | Phylogenetic tips: 112 | Overlap with reference: 24 species | Root age: 219 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r coccinellidae-fig, fig.cap="Validation plots for Coccinellidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Coccinellidae")
```

\newpage

## Chrysomelidae

Chrysomelidae | Higher Taxonomy: Insecta | Chromosomes sampled: 869 | Phylogenetic tips: 1,640 | Overlap with reference: 182 species | Root age: 136 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r chrysomelidae-fig, fig.cap="Validation plots for Chrysomelidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Chrysomelidae")
```

\newpage

## Curculionidae

Curculionidae | Higher Taxonomy: Insecta | Chromosomes sampled: 617 | Phylogenetic tips: 1,492 | Overlap with reference: 33 species | Root age: 95 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r curculionidae-fig, fig.cap="Validation plots for Curculionidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Curculionidae")
```

\newpage

## Tenebrionidae

Tenebrionidae | Higher Taxonomy: Insecta | Chromosomes sampled: 239 | Phylogenetic tips: 318 | Overlap with reference: 40 species | Root age: 180 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r tenebrionidae-fig, fig.cap="Validation plots for Tenebrionidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Tenebrionidae")
```

\newpage

## Drosophilidae

Drosophilidae | Higher Taxonomy: Insecta | Chromosomes sampled: 1,246 | Phylogenetic tips: 685 | Overlap with reference: 352 species | Root age: 62 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r drosophilidae-fig, fig.cap="Validation plots for Drosophilidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Drosophilidae")
```

\newpage

## Lepidoptera

Lepidoptera | Higher Taxonomy: Insecta | Chromosomes sampled: 3,370 | Phylogenetic tips: 2,255 | Overlap with reference: 322 species | Root age: 102 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r lepidoptera-fig, fig.cap="Validation plots for Lepidoptera. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Lepidoptera")
```

\newpage

## Odonata

Odonata | Higher Taxonomy: Insecta | Chromosomes sampled: 703 | Phylogenetic tips: 669 | Overlap with reference: 84 species | Root age: 67 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r odonata-fig, fig.cap="Validation plots for Odonata. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Odonata")
```

\newpage

# Arachnida

## Araneae

Araneae | Higher Taxonomy: Arachnida | Chromosomes sampled: 1,298 | Phylogenetic tips: 897 | Overlap with reference: 87 species | Root age: 350 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r araneae-fig, fig.cap="Validation plots for Araneae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Araneae")
```

\newpage

## Scorpiones

Scorpiones | Higher Taxonomy: Arachnida | Chromosomes sampled: 320 | Phylogenetic tips: 189 | Overlap with reference: 36 species | Root age: 239 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r scorpiones-fig, fig.cap="Validation plots for Scorpiones. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Scorpiones")
```

\newpage

# Mammalia

## Carnivora

Carnivora | Higher Taxonomy: Mammalia | Chromosomes sampled: 167 | Phylogenetic tips: 294 | Overlap with reference: 116 species | Root age: 94 Ma | Taxonomic tips: TRUE | Unresolved: 5.17%

```{r carnivora-fig, fig.cap="Validation plots for Carnivora. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Carnivora")
```

\newpage

## Cetacea

Cetacea | Higher Taxonomy: Mammalia | Chromosomes sampled: 40 | Phylogenetic tips: 90 | Overlap with reference: 34 species | Root age: 34 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r cetacea-fig, fig.cap="Validation plots for Cetacea. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Cetacea")
```

\newpage

## Chiroptera

Chiroptera | Higher Taxonomy: Mammalia | Chromosomes sampled: 204 | Phylogenetic tips: 815 | Overlap with reference: 154 species | Root age: 62 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r chiroptera-fig, fig.cap="Validation plots for Chiroptera. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Chiroptera")
```

\newpage

## Cricetidae

Cricetidae | Higher Taxonomy: Mammalia | Chromosomes sampled: 208 | Phylogenetic tips: 913 | Overlap with reference: 103 species | Root age: 31 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r cricetidae-fig, fig.cap="Validation plots for Cricetidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Cricetidae")
```

\newpage

## Muridae

Muridae | Higher Taxonomy: Mammalia | Chromosomes sampled: 103 | Phylogenetic tips: 913 | Overlap with reference: 57 species | Root age: 24.5 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r muridae-fig, fig.cap="Validation plots for Muridae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Muridae")
```

\newpage

## Primates

Primates | Higher Taxonomy: Mammalia | Chromosomes sampled: 148 | Phylogenetic tips: 455 | Overlap with reference: 90 species | Root age: 74 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r primates-fig, fig.cap="Validation plots for Primates. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Primates")
```

\newpage

## Marsupialia

Marsupialia | Higher Taxonomy: Mammalia | Chromosomes sampled: 40 | Phylogenetic tips: 40 | Overlap with reference: 40 species | Root age: 78 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r marsupialia-fig, fig.cap="Validation plots for Marsupialia. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Marsupialia")
```

\newpage

# Reptilia

## Accipitriformes

Accipitriformes | Higher Taxonomy: Reptilia | Chromosomes sampled: 67 | Phylogenetic tips: 237 | Overlap with reference: 63 species | Root age: 60 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r accipitriformes-fig, fig.cap="Validation plots for Accipitriformes. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Accipitriformes")
```

\newpage

## Galliformes

Galliformes | Higher Taxonomy: Reptilia | Chromosomes sampled: 53 | Phylogenetic tips: 52 | Overlap with reference: 52 species | Root age: 67 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r galliformes-fig, fig.cap="Validation plots for Galliformes. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Galliformes")
```

\newpage

## Gekkonidae

Gekkonidae | Higher Taxonomy: Reptilia | Chromosomes sampled: 73 | Phylogenetic tips: 1,331 | Overlap with reference: 59 species | Root age: 78 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r gekkonidae-fig, fig.cap="Validation plots for Gekkonidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Gekkonidae")
```

\newpage

## Iguania

Iguania | Higher Taxonomy: Reptilia | Chromosomes sampled: 382 | Phylogenetic tips: 1,416 | Overlap with reference: 353 species | Root age: 146 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r iguania-fig, fig.cap="Validation plots for Iguania. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Iguania")
```

\newpage

## Passeriformes

Passeriformes | Higher Taxonomy: Reptilia | Chromosomes sampled: 455 | Phylogenetic tips: 9,189 | Overlap with reference: 449 species | Root age: 64 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r passeriformes-fig, fig.cap="Validation plots for Passeriformes. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Passeriformes")
```

\newpage

## Scincoidea

Scincoidea | Higher Taxonomy: Reptilia | Chromosomes sampled: 154 | Phylogenetic tips: 1,519 | Overlap with reference: 134 species | Root age: 156 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r scincoidea-fig, fig.cap="Validation plots for Scincoidea. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Scincoidea")
```

\newpage

## Serpentes

Serpentes | Higher Taxonomy: Reptilia | Chromosomes sampled: 256 | Phylogenetic tips: 1,877 | Overlap with reference: 213 species | Root age: 124 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r serpentes-fig, fig.cap="Validation plots for Serpentes. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Serpentes")
```

\newpage

## Testudines

Testudines | Higher Taxonomy: Reptilia | Chromosomes sampled: 141 | Phylogenetic tips: 286 | Overlap with reference: 122 species | Root age: 201 Ma | Taxonomic tips: TRUE | Unresolved: 3.28%

```{r testudines-fig, fig.cap="Validation plots for Testudines. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Testudines")
```

\newpage

# Amphibia

## Caudata

Caudata | Higher Taxonomy: Amphibia | Chromosomes sampled: 246 | Phylogenetic tips: 796 | Overlap with reference: 204 species | Root age: 415 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r caudata-fig, fig.cap="Validation plots for Caudata. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Caudata")
```

\newpage

## Anura

Anura | Higher Taxonomy: Amphibia | Chromosomes sampled: 1,831 | Phylogenetic tips: 5,326 | Overlap with reference: 1,207 species | Root age: 210 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r anura-fig, fig.cap="Validation plots for Anura. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Anura")
```

\newpage

# Actinopterygii

## Anabantiformes

Anabantiformes | Higher Taxonomy: Actinopterygii | Chromosomes sampled: 61 | Phylogenetic tips: 196 | Overlap with reference: 41 species | Root age: 73 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r anabantiformes-fig, fig.cap="Validation plots for Anabantiformes. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Anabantiformes")
```

\newpage

## Cichlidae

Cichlidae | Higher Taxonomy: Actinopterygii | Chromosomes sampled: 281 | Phylogenetic tips: 750 | Overlap with reference: 88 species | Root age: 60 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r cichlidae-fig, fig.cap="Validation plots for Cichlidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Cichlidae")
```

\newpage

## Nothobranchiidae

Nothobranchiidae | Higher Taxonomy: Actinopterygii | Chromosomes sampled: 242 | Phylogenetic tips: 11,638 | Overlap with reference: 79 species | Root age: 73 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r nothobranchiidae-fig, fig.cap="Validation plots for Nothobranchiidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Nothobranchiidae")
```

\newpage

## Gobiidae

Gobiidae | Higher Taxonomy: Actinopterygii | Chromosomes sampled: 232 | Phylogenetic tips: 827 | Overlap with reference: 65 species | Root age: 52 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r gobiidae-fig, fig.cap="Validation plots for Gobiidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Gobiidae")
```

\newpage

## Siluriformes

Siluriformes | Higher Taxonomy: Actinopterygii | Chromosomes sampled: 165 | Phylogenetic tips: 2,009 | Overlap with reference: 131 species | Root age: 96 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r siluriformes-fig, fig.cap="Validation plots for Siluriformes. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Siluriformes")
```

\newpage

## Characidae

Characidae | Higher Taxonomy: Actinopterygii | Chromosomes sampled: 663 | Phylogenetic tips: 1,019 | Overlap with reference: 238 species | Root age: 108 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r characidae-fig, fig.cap="Validation plots for Characidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Characidae")
```

\newpage

## Cyprinidae

Cyprinidae | Higher Taxonomy: Actinopterygii | Chromosomes sampled: 1,111 | Phylogenetic tips: 1,368 | Overlap with reference: 398 species | Root age: 90 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r cyprinidae-fig, fig.cap="Validation plots for Cyprinidae. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Cyprinidae")
```

\newpage

# Chondrichthyes

## Chondrichthyes

Chondrichthyes | Higher Taxonomy: Chondrichthyes | Chromosomes sampled: 176 | Phylogenetic tips: 1,192 | Overlap with reference: 77 species | Root age: 413 Ma | Taxonomic tips: FALSE | Unresolved: N/A

```{r chondrichthyes-fig, fig.cap="Validation plots for Chondrichthyes. (A) Continuous character map of haploid chromosome number across the phylogeny. (B) Prior versus posterior density distributions for dysploidy rate. (C) Posterior predictive simulation adequacy test for variance. (D) Posterior predictive simulation adequacy test for Shannon's entropy."}
create_panel_figure("Chondrichthyes")
```
